\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-10 fully-abstract-comp/popl2019/paper.tex
Full abstraction discussion (1st draft)

\section{Discussion}
\label{sec:discussion}
% \begin{itemize}
% \item explain how fully abstract overlay semantics could form one pass of a verified secure compiler.
% \item Sharing stack references accross component boundaries is supported
% \item Other notions of well-bracketedness (specifically one would be to allow different stacks)
% \end{itemize}
\subsection{Full abstraction}
% - Full abstraction proofs difficult

>>>>

\section{Discussion}
\label{sec:discussion}
% \begin{itemize}
% \item explain how fully abstract overlay semantics could form one pass of a verified secure compiler.
% \item Sharing stack references accross component boundaries is supported
% \item Other notions of well-bracketedness (specifically one would be to allow different stacks)
% \end{itemize}
\subsection{Full abstraction}
% - Full abstraction proofs difficult
In the grand scheme of proving full abstraction from a high-level language to assembly, we believe \stktokens{} can play a role.
The target of a fully-abstract compiler must have enforcement mechanisms that can enforce the properties of the high-level language.
As demonstrated in this paper, a capability machine with linear capabilities can enforce two such properties namely LSE and WBCF.
Further due to the modularity of full-abstraction proofs, fully abstract compilers from languages with LSE and WBCF can target \srccm{} directly and rely on the full-abstraction proof this paper presents.
However in order for a fully abstract compiler utilise our full-abstraction proof, it must satisfy the conditions of the proof, namely the compiled code must be well-formed and well-behaved.
From a high-level perspective this condition actually says that the compiled code does not need to protect itself from itself which it would have to without the condition.

When creating fully-abstract compilers between low-level machines, it is a big challenge to work with the exposed addresses.
In particular, if the compilation changes the code size of a block of code, then it may be observable and prevent full-abstraction from being proven.
We would argue that when a compilation reaches a phase where addresses are exposed, then the compilation should no longer change the code.
This does, however, pose the challenge that there might quite a few abstractions in difference between the language where addresses are hidden to a machine where they are not.
We propose that this challenge is solved by implementing these abstractions in a number of overlay semantics.
By implementing them one by one, one can deal with one abstraction at a time reducing the complexity of each necessary full-abstraction proof.
